Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-23 ms.qmd
Add in updated figure for supp for predictability. Added some mored for plotting and fixed up Fig S2 legend

#################################################
### Same model as above, but seperate for habitat 
### For plotting, 4.8
#################################################

if(rerun){
  # Terrestrial Models
    model4.8_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 + max_temp_c| spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild_acclim_t)
    saveRDS(model4.8_t, "./output/models/model4.8_t")
} else {
     model4.8_t <- readRDS("./output/models/model4.8_t")
     model4.8_m <- readRDS("./output/models/model4.8_m")
     model4.8_f <- readRDS("./output/models/model4.8_f")
}

@@

####################
# lnRR ACF
####################
 dat_textacf <- data.frame(label = c(text(slope_f_3.8), 
                                     text(slope_m_3.8), 
                                     text(slope_t_3.8)),
                          label2 = c(text(slope_f_3.8, b = FALSE), 
                                     text(slope_m_3.8, b = FALSE), 
                                     text(slope_t_3.8, b = FALSE)),
                               p = c(p_text(slope_f_3.8), 
                                     p_text(slope_m_3.8), 
                                     p_text(slope_t_3.8)),
                           title = c("Freshwater", "Marine", "Terrestrial"), 
                       condition = c("f", "m", "t"),
                               x = rep(0, 3))
y_adj = -3
# Terrestrial
  p_t_rr_acf <-  bubble_plot(model3.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_t, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[3], colour = "black", stroke = 0.2, shape = 21) + labs(title = dat_text$title[3]) +
  annotate("text", x = dat_text$x[3], y = y_adj, label = TeX(dat_text$p[3]), size = 8) +
  annotate("text", x = dat_text$x[3], y = y_adj + 0.5, label = TeX(dat_text$label2[3]), size = 8) +
  annotate("text", x = dat_text$x[3], y = y_adj + 1, label = TeX(dat_text$label[3]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3,3)

# Marine
p_m_rr_acf <-  bubble_plot(model3.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Predictability", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_m, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[2], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[2]) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj, label = TeX(dat_text$p[2]), size = 8) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+0.5, label = TeX(dat_text$label2[2]), size = 8) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+1, label = TeX(dat_text$label[2]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)

# Freshwater
p_f_rr_acf <-  bubble_plot(model3.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Predictability", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[1]) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj, label = TeX(dat_text$p[1]), size = 8) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+0.5, label = TeX(dat_text$label2[1]), size = 8) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+ 1, label = TeX(dat_text$label[1]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)

####################
# lnCVR CV
####################
dat_textcvr_acf <- data.frame(label = c(text(slope_f_4.8), 
                                 text(slope_m_4.8), 
                                 text(slope_t_4.8)),
                      label2 = c(text(slope_f_4.8, b = FALSE), 
                                 text(slope_m_4.8,b = FALSE), 
                                 text(slope_t_4.8,b = FALSE)),
                           p = c(p_text(slope_f_4.8), 
                                 p_text(slope_m_4.8), 
                                 p_text(slope_t_4.8)),
                       title = c("Freshwater", "Marine", "Terrestrial"), 
                      condition = c("f", "m", "t"),
                      x = rep(0, 3),
                      y = rep(-4, 3))

# Freshwater
  yadj2 = -6
  x_f = 0.6
  p_f_cv_acf <-  bubble_plot( , mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
                              xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
      geom_point(data = lnCVRQ10_data_wild_acclim_f, 
                 aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
                 fill = col[1], colour = "black", stroke = 0.2, shape = 21) + 
    annotate("text", x = dat_textcvr_acf$x[1]+x_f, y = yadj2, label = TeX(dat_textcvr_acf$p[1]), size = 8) +
    annotate("text", x = dat_textcvr_acf$x[1]+x_f, y = yadj2+0.8, label = TeX(dat_textcvr_acf$label2[1]), size = 8) +
    annotate("text", x = dat_textcvr_acf$x[1]+x_f, y = yadj2+1.6, label = TeX(dat_textcvr_acf$label[1]), size = 8) +
  theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
        axis.title = element_text(size = size_axis), 
        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
    ylim(-6, 3.5)

# Marine
  x_m = -0.4
  p_m_cv_acf <-  bubble_plot( , mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
                              xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
    geom_point(data = lnCVRQ10_data_wild_acclim_m, 
                 aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
                 fill = col[2], colour = "black", stroke = 0.2, shape = 21) + 
    annotate("text", x = dat_textcvr_acf$x[1]+x_m, y = yadj2, label = TeX(dat_textcvr_acf$p[2]), size = 8) +
    annotate("text", x = dat_textcvr_acf$x[1]+x_m, y = yadj2+0.8, label = TeX(dat_textcvr_acf$label2[2]), size = 8) +
    annotate("text", x = dat_textcvr_acf$x[1]+x_m, y = yadj2+1.6, label = TeX(dat_textcvr_acf$label[2]), size = 8) +
    theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
        axis.title = element_text(size = size_axis), 
        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
    ylim(-6, 3.5)

x_t = 0
p_t_cv_acf <-  bubble_plot( , mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
                            xlab = "Thermal Predictability", g = FALSE, k = FALSE) + 
  geom_point(data = lnCVRQ10_data_wild_acclim_t, 
               aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
               fill = col[3], colour = "black", stroke = 0.2, shape = 21) +
  annotate("text", x = dat_textcvr_acf$x[3]+x_t, y = yadj2, label = TeX(dat_textcvr_acf$p[3]), size = 8) +
  annotate("text", x = dat_textcvr_acf$x[3]+x_t, y = yadj2+0.8, label = TeX(dat_textcvr_acf$label2[3]), size = 8) +
  annotate("text", x = dat_textcvr_acf$x[3]+x_t, y = yadj2+1.6, label = TeX(dat_textcvr_acf$label[3]), size = 8) +
  theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
  ylim(-6, 3.5)

@@

p_cv_acf <- (p_t_rr_acf + p_m_rr_acf + p_f_rr_acf) / (p_t_cv_acf + p_m_cv_acf + p_f_cv_acf) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))

ggsave(p_cv_acf, width = 18, height = 10, filename = "./output/figures/fig_p_cv_acf_r1.pdf")

  p_cv <- image_read("./output/figures/fig_p_cv_r1.png")
  p_cv 
```
#### *Publication bias analysis*

@@

```{r, pubias}
#| label: pubias
#| echo: false
#| include: false
rerun = FALSE
if(rerun){
  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)

  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)

  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category  + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)

@@

```{r, fig-s2}
#| label: fig-s2
#| fig-cap: Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B)log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$). Both acute ('green') and acclimation ('orange') effect sizes are plotted.
cols <- c("#303234", "#D3D3D3")
ps2_1 <- ggplot(lnRRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnRR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none") + scale_color_manual(name = "Type", values = cols)

>>>>

#################################################
### Same model as above, but seperate for habitat 
### For plotting, 4.8
#################################################
 lnCVRQ10_data_wild_acclim_t <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "t")
 lnCVRQ10_data_wild_acclim_m <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "m")
 lnCVRQ10_data_wild_acclim_f <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "f")

if(rerun){
  # Terrestrial Model
    model4.8_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 + max_temp_c| spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild_acclim_t)
    saveRDS(model4.8_t, "./output/models/model4.8_t")

  # Freshwater Model
    model4.8_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 + max_temp_c| spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild_acclim_f)
    saveRDS(model4.8_f, "./output/models/model4.8_f")

  # Marine Model
    model4.8_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 + max_temp_c| spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild_acclim_m)
    saveRDS(model4.8_m, "./output/models/model4.8_m")
} else {
     model4.8_t <- readRDS("./output/models/model4.8_t")
     model4.8_m <- readRDS("./output/models/model4.8_m")
     model4.8_f <- readRDS("./output/models/model4.8_f")
}

@@

####################
# lnRR ACF
####################
 dat_textacf <- data.frame(label = c(text(slope_f_3.8), 
                                     text(slope_m_3.8), 
                                     text(slope_t_3.8)),
                          label2 = c(text(slope_f_3.8, b = FALSE), 
                                     text(slope_m_3.8, b = FALSE), 
                                     text(slope_t_3.8, b = FALSE)),
                               p = c(p_text(slope_f_3.8), 
                                     p_text(slope_m_3.8), 
                                     p_text(slope_t_3.8)),
                           title = c("Freshwater", "Marine", "Terrestrial"), 
                       condition = c("f", "m", "t"),
                               x = rep(0, 3))
  y_adj = -3
#############
# Terrestrial
#############
  p_t_rr_acf <-  bubble_plot(model3.8_t, mod = "acf_lag1_c", group = "spp", 
                             ylab = TeX("$lnRR_{Q_{10_{acclim}}}$"), 
                             xlab = "Thermal Predictability", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_t, 
               aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
               fill = col[3], colour = "black", stroke = 0.2, shape = 21) + 
    labs(title = dat_textacf$title[3]) +
    annotate("text", x = dat_textacf$x[3], y = y_adj, label = TeX(dat_textacf$p[3]), size = 8) +
    annotate("text", x = dat_textacf$x[3], y = y_adj + 0.5, label = TeX(dat_text$label2[3]), size = 8) +
    annotate("text", x = dat_textacf$x[3], y = y_adj + 1, label = TeX(dat_textacf$label[3]), size = 8) +
    theme( axis.text = element_text(size = size_axis), 
         axis.text.y = element_text(size = size_axis), 
          axis.title = element_text(size = size_axis),
        axis.title.x = element_blank(),
          plot.title = element_text( size = 36, hjust = 0)) + 
    ylim(-3,3)
#############
# Marine
#############
  x_m = -2.5
p_m_rr_acf <-  bubble_plot(model3.8_m, mod = "acf_lag1_c", group = "spp", 
                           ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), 
                           xlab = "Thermal Predictability", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_m, 
               aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
               fill = col[2], colour = "black", stroke = 0.2, shape = 21) +  
    labs(title = dat_textacf$title[2]) +
    annotate("text", x = dat_textacf$x[2]+x_m, y = y_adj,     label = TeX(dat_textacf$p[2]),      size = 8) +
    annotate("text", x = dat_textacf$x[2]+x_m, y = y_adj+0.5, label = TeX(dat_textacf$label2[2]), size = 8) +
    annotate("text", x = dat_textacf$x[2]+x_m, y = y_adj+1,   label = TeX(dat_textacf$label[2]),  size = 8) +
    theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
         axis.title = element_text(size = size_axis), 
       axis.title.x = element_blank(),
         plot.title = element_text( size = 36, hjust = 0)) + 
    ylim(-3, 3)

#############
# Freshwater
#############
x_f = -0.2
p_f_rr_acf <-  bubble_plot(model3.8_f, mod = "acf_lag1_c", group = "spp", 
                           ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), 
                           xlab = "Thermal Predictability", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_f, 
               aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
               fill = col[1], colour = "black", stroke = 0.2, shape = 21) +  
    labs(title = dat_textacf$title[1]) +
    annotate("text", x = dat_textacf$x[1]+x_f, y = y_adj,     label = TeX(dat_textacf$p[1]),      size = 8) +
    annotate("text", x = dat_textacf$x[1]+x_f, y = y_adj+0.5, label = TeX(dat_textacf$label2[1]), size = 8) +
    annotate("text", x = dat_textacf$x[1]+x_f, y = y_adj+ 1,  label = TeX(dat_textacf$label[1]),  size = 8) +
    theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
         axis.title = element_text(size = size_axis), 
       axis.title.x = element_blank(),
         plot.title = element_text( size = 36, hjust = 0)) + 
    ylim(-3, 3)

####################
# lnCVR CV
####################
dat_textcvr_acf <- data.frame(label = c(text(slope_f_4.8), 
                                 text(slope_m_4.8), 
                                 text(slope_t_4.8)),
                      label2 = c(text(slope_f_4.8, b = FALSE), 
                                 text(slope_m_4.8,b = FALSE), 
                                 text(slope_t_4.8,b = FALSE)),
                           p = c(p_text(slope_f_4.8), 
                                 p_text(slope_m_4.8), 
                                 p_text(slope_t_4.8)),
                       title = c("Freshwater", "Marine", "Terrestrial"), 
                      condition = c("f", "m", "t"),
                      x = rep(0, 3),
                      y = rep(-4, 3))
#############
# Freshwater
#############
  yadj2 = -6
  x_f = -0.2
  p_f_cv_acf <-  bubble_plot(model4.8_f, mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
                              xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
      geom_point(data = lnCVRQ10_data_wild_acclim_f, 
                 aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
                 fill = col[1], colour = "black", stroke = 0.2, shape = 21) + 
    annotate("text", x = dat_textcvr_acf$x[1]+x_f, y = yadj2, label = TeX(dat_textcvr_acf$p[1]), size = 8) +
    annotate("text", x = dat_textcvr_acf$x[1]+x_f, y = yadj2+0.8, label = TeX(dat_textcvr_acf$label2[1]), size = 8) +
    annotate("text", x = dat_textcvr_acf$x[1]+x_f, y = yadj2+1.6, label = TeX(dat_textcvr_acf$label[1]), size = 8) +
  theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
        axis.title = element_text(size = size_axis), 
        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
    ylim(-6, 3.5)
#############
# Marine
#############
  x_m = -2.5
  p_m_cv_acf <-  bubble_plot(model4.8_m, mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
                              xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
    geom_point(data = lnCVRQ10_data_wild_acclim_m, 
                 aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
                 fill = col[2], colour = "black", stroke = 0.2, shape = 21) + 
    annotate("text", x = dat_textcvr_acf$x[1]+x_m, y = yadj2, label = TeX(dat_textcvr_acf$p[2]), size = 8) +
    annotate("text", x = dat_textcvr_acf$x[1]+x_m, y = yadj2+0.8, label = TeX(dat_textcvr_acf$label2[2]), size = 8) +
    annotate("text", x = dat_textcvr_acf$x[1]+x_m, y = yadj2+1.6, label = TeX(dat_textcvr_acf$label[2]), size = 8) +
    theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
        axis.title = element_text(size = size_axis), 
        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
    ylim(-6, 3.5)
#############
# Terrestrial
#############
x_t = -0.2
p_t_cv_acf <-  bubble_plot(model4.8_t, mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
                            xlab = "Thermal Predictability", g = FALSE, k = FALSE) + 
  geom_point(data = lnCVRQ10_data_wild_acclim_t, 
               aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
               fill = col[3], colour = "black", stroke = 0.2, shape = 21) +
  annotate("text", x = dat_textcvr_acf$x[3]+x_t, y = yadj2, label = TeX(dat_textcvr_acf$p[3]), size = 8) +
  annotate("text", x = dat_textcvr_acf$x[3]+x_t, y = yadj2+0.8, label = TeX(dat_textcvr_acf$label2[3]), size = 8) +
  annotate("text", x = dat_textcvr_acf$x[3]+x_t, y = yadj2+1.6, label = TeX(dat_textcvr_acf$label[3]), size = 8) +
  theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
  ylim(-6, 3.5)

@@

p_acf <- (p_t_rr_acf + p_m_rr_acf + p_f_rr_acf) / (p_t_cv_acf + p_m_cv_acf + p_f_cv_acf) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))

ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/fig_p_acf_r1.pdf")

  p_acf <- image_read("./output/figures/fig_p_acf_r1.png")
  p_acf 
```
#### *Publication bias analysis*

@@

```{r, pubias}
#| label: pubias
#| echo: false
#| include: false
rerun = FALSE
if(rerun){
  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)

  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + V + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)

  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + V + habitat*life.hist*type + trait_category  + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)

@@

```{r, fig-s2}
#| label: fig-s2
#| fig-cap: Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B) log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$). Both acute ('black') and acclimation ('grey') effect sizes are plotted.
cols <- c("#303234", "#D3D3D3")
ps2_1 <- ggplot(lnRRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnRR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none") + scale_color_manual(name = "Type", values = cols)
